---
title: 'Paper Wrapper: Domain General Metacognition'
output:
  word_document: default
  html_notebook: default
---

Setup

```{r}
# clean slate to be sure
rm(list = ls())
if (!require("here")) install.packages("here")
source(here("r", "setup_depends.R"))
source(here("r", "bootcormat.R")) 

# set apa theme for plots
apatheme=theme_bw()+ #theme
  theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        panel.border=element_blank(),
        axis.line=element_line(),
        text = element_text(size = 15),
        axis.title = element_text(size = 12))



# spider-man color palette

colors = c("#DF1F2D", "#B11313", "#2B3784", "#447BBE")
```

Data import
```{r}

source(here("r", "metacog_data_import.R")) # imports data and runs trial level exclusions from the prereg. 

head(metadata)

```


Load or fit the MLE model (if it does not exist).

```{r}

subjects = unique(metadata$subject) # subjects vector, for looping
modalities = as.character(unique(metadata$modality)) # modalities vector, for looping


fit_filename = here("data_summary", "mle_fitdata.Rda")

if (file.exists(fit_filename) == 1 ) {

load(fit_filename)
  
}else  {
  
source(here("r", "fit_mle_loop.R"))

  }

head(mle_fit_data)
```

Run group level exclusions based on ML and create plots: 

```{r}

# script to run all group level exclusions
source(here("r", "mle_fitdata_exclude.R")) 

# da plot
p1+p2
# c plot
p3+p4
# mratio plot
p5+p6
# median contrast
p7+p8

```

Pivot the MLE data frame to wide. 
```{r}


mle_wdata_exclude <- mle_metadata_exc %>% pivot_wider(
  names_from = modality,
  values_from = c(da, mda, mratio, c, avg_conf, medContrast)
)


write.csv(mle_wdata_exclude, file = here("data_summary","mle_fit_data_wide.csv"))

head(mle_wdata_exclude)


#Average everything and calculate standard deviations for the MLE model: 
metadata_avg <- mle_metadata_exc %>% 
  group_by(modality) %>% 
  summarise(dprime=mean(da, na_rm=TRUE), 
            criterion=mean(c, na_rm=TRUE),
            metad=mean(mda, na_rm=TRUE),
            mratio1=mean(mratio, na_rm=TRUE),
            avg_conf1=mean(avg_conf, na_rm=TRUE),
            dprime_sd=sd(da),
            criterion_sd=sd(c),
            metad_sd=sd(mda),
            mratio_sd=sd(mratio),
            avg_conf_sd=sd(avg_conf), 
            n1 = n()
            )  %>% mutate(Modality=c("Calories", "GDP", "Memory", "Vision")) %>%
  select(-modality)
```

Create Figure 2: summary of basic variables

```{r}

source(here("r", "1_figure2.R"))

figure2

ggsave(here("figs", "Figure2.png"), height = 16.8, width = 16.8, units = "cm", dpi = 300)  


```



Now run the bootstrapped Spearman's correlations, for preregistered hypothesis tests.

```{r}

# cognitive sensitivity - dprime

corrdat <- mle_wdata_exclude %>%
  na.omit() %>%
  select(starts_with("da"))

apa.bootcor.table(corrdat, filename=here("tables", "da_bootCorr_table.doc"))

# average confidence - metabias 

corrdat <- mle_wdata_exclude %>%
  na.omit() %>%
  select(starts_with("avg_conf"))

apa.bootcor.table(corrdat, filename=here("tables", "conf_bootCorr_table.doc"))

# metacognitive sensitivity 

corrdat <- mle_wdata_exclude %>%
  na.omit() %>%
  select(starts_with("mda"))

apa.bootcor.table(corrdat, filename=here("tables", "MDA_bootCorr_table.doc"))

# metacognitive efficiency
corrdat <- mle_wdata_exclude %>%
  na.omit() %>%
  select(starts_with("mratio"))

apa.bootcor.table(corrdat, filename=here("tables", "mratio_bootCorr_table.doc"))

#mda_results <- bootcormat(corrdat)



```

Next we will fit (or load) the hierarchical metacognition model 

```{r}
# these next lines will download the fitted model file from the project
# open science foundation (OSF) repository. Because the files are too large for github
# (around 250 mb), we download them to a local directory. The /osf directory the files are # # downloaded too is included in the .gitignore file ensuring it is only created locally.

# check if already exists to avoid redownloading

fit_filename = here("osf/HMM", "modelfit.RDS")

if (file.exists(fit_filename) == 1 ) {

output <- readRDS(fit_filename)


} else {

# download file 
osf_project <- osf_retrieve_node("https://osf.io/u6sf2/")

download_path <- here("osf")
osf_files <- osf_ls_files(osf_project)

osf_download(osf_files, path = download_path)
  
output <- readRDS(fit_filename)
}

# if you wish to refit the model yourself, you can instead uncomment the following line:
# note this will take several hours to run... 
# source(here("r", "fit_Hmetad.R"))
# output <- metad_groupcorr(nR_S1, nR_S2)

```

```{r}

## Model output ------------------------------------------------------------
# note that this section can take a while to run and creates a lot of large variables.

# Convergence diagnostic
Value <- gelman.diag(output, confidence = 0.95)
Rhat <- data.frame(conv = Value$psrf)

# Values (mean and CI)
Value <- summary(output)
stat <- data.frame(mean = Value$statistics[,"Mean"])
stat %<>%
  rownames_to_column(var = "name") %>% 
  cbind(CILow = Value$quantiles[,"2.5%"]) %>% 
  cbind(CIUp = Value$quantiles[,"97.5%"])

# HDI function 
HDI <- data.frame(HPDinterval(output, prob = 0.95))
HDI %<>%
  rownames_to_column(var = "name")


## Plot trace mcmc ---------------------------------------------------------
# creates many plots and takes a long time to run... uncomment to see sampling traces
# traceplot(output)

## Plot posterior distributions -------------------------------------------------------------------
mcmc.sample <- ggs(output)

```

```{r}
source(here("r", "plot_hmm_mratios.R"))


(memPlot | calPlot) / (gdpPlot | visPlot)
# Plot posterior distribution for rho value

ggsave(here("figs", "sup_fig1_hmm_mratio.png"))
```

Here we plot the same, but for the correlation (rho) estimate for each condition

```{r}
#calculate mean rho for each plot
mcmc.rho <- mcmc.sample %>% 
  filter(Parameter == "rho[1]"| Parameter == "rho[2]"| Parameter == "rho[3]"| Parameter == "rho[4]"| Parameter == "rho[5]"| Parameter == "rho[6]")

meanRho <- mcmc.rho %>% group_by(Parameter) %>% summarise(value= mean(value, na.rm=TRUE)) 

# Report the mean rho for each plot
H1title <- paste("Rho =",round(meanRho$value[1], digits=3)) #Mem-Cal
H2title <- paste("Rho =",round(meanRho$value[2], digits=3)) #Mem-GDP
H3title <- paste("Rho =",round(meanRho$value[3], digits=3)) #Mem-Vis
H4title <- paste("Rho =",round(meanRho$value[4], digits=3)) #Cal-GDP
H5title <- paste("Rho =",round(meanRho$value[5], digits=3)) #Cal-vis
H6title <- paste("Rho =",round(meanRho$value[6], digits=3)) #GDP-Vis

#filter to get relevant data for each plot
Rho1 <- mcmc.sample %>% filter(Parameter == "rho[1]") 
Rho2 <- mcmc.sample %>% filter(Parameter == "rho[2]") 
Rho3 <- mcmc.sample %>% filter(Parameter == "rho[3]") 
Rho4 <- mcmc.sample %>% filter(Parameter == "rho[4]") 
Rho5 <- mcmc.sample %>% filter(Parameter == "rho[5]") 
Rho6 <- mcmc.sample %>% filter(Parameter == "rho[6]") 

## MAke plots
R1 <- RhoPlot(Rho1, "rho[1]", HDI, stat) + labs(title = "Memory vs Calories", subtitle= paste(H1title))
R2 <- RhoPlot(Rho2, "rho[2]", HDI, stat) + labs(title = "Memory vs GDP", subtitle= paste(H2title))
R3 <- RhoPlot(Rho3, "rho[3]", HDI, stat) + labs(title = "Memory vs Vision", subtitle= paste(H3title))
R4 <- RhoPlot(Rho4, "rho[4]", HDI, stat) + labs(title = "GDP vs Calories", subtitle= paste(H4title))
R5 <- RhoPlot(Rho5, "rho[5]", HDI, stat) + labs(title = "Calories vs Vision", subtitle= paste(H5title))
R6 <- RhoPlot(Rho6, "rho[6]", HDI, stat) + labs(title = "GDP vs Vision", subtitle= paste(H6title))


#Bayesian Hierarchical fit: combine plots
RhoPlot <- ggarrange(R1, R3, R2, R6, R4, R5)
annotate_figure(RhoPlot, top = text_grob("Hierarchical Bayesian Estimation", color = "black", face = "bold", size = 14)) 

ggsave(here("figs", "sup_fig2_mrho_grid.png"), height = 7, width = 12)
```

```{r}

# Create individual Mratio data frame
Mratio_indiv <- stat %>% 
  filter(grepl("^M", name)) %>% 
  mutate(task = ifelse(grepl("1]", name), "Mem",
                       ifelse(grepl("2]", name), "Cal",
                              ifelse(grepl("3]", name), "GDP","Vis"))),
         pp = name %>%
           str_extract(regex("\\d+(?=,)")) %>% 
           as.integer()) %>% 
  dcast(pp ~ task, value.var = "mean")

# Create plot

Cor1 <- ind_hier(Mratio_indiv, Mratio_indiv$Mem,Mratio_indiv$Cal) +
  scale_y_continuous("Calories") + scale_x_continuous("Memory") +
  ggtitle(H1title)+ theme(plot.title = element_text( size = 13))


Cor2 <- ind_hier(Mratio_indiv, Mratio_indiv$Mem, Mratio_indiv$GDP) +
  ggtitle(H2title)+ theme(plot.title = element_text( size = 13)) +
  scale_y_continuous("GDP") + scale_x_continuous("Memory")

Cor3 <- ind_hier(Mratio_indiv, Mratio_indiv$Mem, Mratio_indiv$Vis)+
  ggtitle(H3title)+ theme(plot.title = element_text( size = 13)) +
  scale_y_continuous("Vis") + scale_x_continuous("Memory") 

Cor4 <- ind_hier(Mratio_indiv, Mratio_indiv$Cal, Mratio_indiv$GDP)+
  ggtitle(H4title)+ theme(plot.title = element_text( size = 13)) +
  scale_y_continuous("GDP") + scale_x_continuous("Calories") 

Cor5 <- ind_hier(Mratio_indiv, Mratio_indiv$Cal, Mratio_indiv$Vis)+
  ggtitle(H5title)+ theme(plot.title = element_text( size = 13)) +
  scale_y_continuous("Vision") + scale_x_continuous("Calories") 

Cor6 <- ind_hier(Mratio_indiv, Mratio_indiv$GDP, Mratio_indiv$Vis)+
  ggtitle(H6title) + theme(plot.title = element_text( size = 13)) +
  scale_y_continuous("Vision") + scale_x_continuous("GDP") 
    
IndPlotHier <- ggarrange(Cor1, Cor2, Cor3, Cor6, Cor4, Cor5) 
annotate_figure(IndPlotHier, top = text_grob("Hierarchical Bayesian Model", color = "black", 
                                         face = "bold", size = 18))   


ggsave(here("figs", "Hier_Rho_scatter.png"), height = 7, width = 12)


```

Now we will combine data from the MLE and HMM fits to create one overall plot (figure 3)

```{r}
source(here("r", "shrinkplot_Hmm.R"))
shrinkplot

#The figure can be found in the folder called 'figs' and is called shrinkage_all_plot. 
```


Create a table with the HMM M-ratio results

```{r}
#Fit stats summary. 
Fit <- stat %>%
   cbind(lower = HDI$lower,
         upper = HDI$upper,
        Rhat = Rhat[,1]) 

#Select Mratio and take the exponential of the value:
meanMratio <- Fit %>% filter(str_detect(name,"mu_logMratio")) %>%
  mutate(Hmratio=exp(mean), 
         lowerHDI=exp(lower),
         upperHDI=exp(upper)) %>% 
    mutate(Modality=c("Memory", "Calories", "GDP", "Vision"), 
           n2="319") %>%
  select(Modality, Hmratio, lowerHDI, upperHDI, n2)


# select the HDIs for each rho  
rHDI <- HDI %>% filter(str_detect(name,"rho")) %>% select(name, lower, upper)
#join these HDIs with mean rho
RhoHDI <- full_join(meanRho, rHDI, 
                    by= c("Parameter"="name"))

#Change names and layout: 
table4 <- RhoHDI %>% mutate(Pair= c("Memory & Calories", "Memory and GDP", "Memory and Vision", 
                                    "GDP and Calories", "Calories and Vision", "GDP and Vision"),
                            Rho=round(value,3),
                            HDIr = paste(round(lower,3), round(upper,3), sep=" ; "))

table4 <- table4 %>% mutate(HDI = paste0("[", table4$HDIr, "]"))


#Load criterion and dprime 
c1 <-readRDS(here("osf/HMM", "fit_c1"))
d1 <-readRDS(here("osf/HMM", "fit_d1"))

#Label tasks and pivot the vectors: 
c1 <- data.frame(c1)
d1 <- data.frame(d1)
c1 <- c1 %>% mutate (Memory=T1, Calories= T2, GDP = T3, Vision = T4, subject = row_number())%>% select(-T1, -T2, -T3, -T4)
d1 <- d1 %>% mutate (Memory=T1, Calories= T2, GDP = T3, Vision = T4, subject = row_number())%>% select(-T1, -T2, -T3, -T4)

c1l <- c1 %>% pivot_longer(
  cols = c("Memory", "Calories", "GDP", "Vision"), 
  names_to="Modality",
  values_to ="Criterion")

d1l <- d1 %>% pivot_longer(
  cols = c("Memory", "Calories", "GDP", "Vision"), 
  names_to="Modality",
  values_to ="d'")

#Summarise - mean and SD: 
c1l_avg <- c1l %>% 
  group_by(Modality) %>% 
  summarise(Hcriterion=mean(Criterion, na_rm=TRUE), 
            Hcriterion_sd=sd(Criterion), n3=n())

d1l_avg <- d1l %>% 
  group_by(Modality) %>% 
  summarise(Hdprime=mean(`d'`, na_rm=TRUE), 
            Hdprime_SD= sd(`d'`), n4=n())

#Join the two: 
HdcSum <- left_join(c1l_avg , d1l_avg , 
                     by=c("Modality"="Modality"))

#Joim Hier cognitive and metacognitive: 
MetaHier<- left_join(meanMratio , HdcSum , 
                     by=c("Modality"="Modality"))

#Join MLE and Hier: 
MetaSum <- left_join(MetaHier , metadata_avg , 
                     by=c("Modality"="Modality"))



#HDI for mean mratio: 
meanMratio1 <- MetaSum %>% mutate(HDIr = paste(round(lowerHDI,3), round(upperHDI,3), sep=" ; "))
meanMratio1  <- meanMratio1  %>% mutate(HDI = paste0("[", meanMratio1$HDIr, "]"))

HMT <- data.frame((matrix(NA, nrow=4, ncol=7)))
HMT [,1] <-meanMratio1$Modality
HMT [,2] <-paste0(round(meanMratio1$Hmratio,2))
HMT [,3] <-meanMratio1$HDI

colnames(HMT) <- c("Variable", "M", "95% HDI", "Memory", "Calorie", "GDP", "Vision")

HMT [2,4] <- paste0(round(table4[table4[,5] == "Memory & Calories",6],3), " ",
                    table4[table4[,5] == "Memory & Calories",8]) 
HMT [3,4] <- paste0(round(table4[table4[,5] == "Memory and GDP",6],3), " ",
                    table4[table4[,5] == "Memory and GDP",8]) 
HMT [4,4] <- paste0(round(table4[table4[,5] == "Memory and Vision",6],3), " ",
                    table4[table4[,5] == "Memory and Vision",8]) 
HMT [3,5] <- paste0(round(table4[table4[,5] == "GDP and Calories",6],3), " ",
                    table4[table4[,5] == "GDP and Calories",8]) 
HMT [4,5] <- paste0(round(table4[table4[,5] == "Calories and Vision",6],3), " ",
                    table4[table4[,5] == "Calories and Vision",8]) 
HMT [4,6] <- paste0(round(table4[table4[,5] == "GDP and Vision",6],3), " ",
                    table4[table4[,5] == "GDP and Vision",8]) 


HMT[is.na(HMT)] <- ""

  
```

```{r}

print_table <- nice_table(HMT, 
           title = c("Table X", "Means, 95% High Density Intervals (HDI), and estimated between-task correlations with 95% HDIs"),
           footnote = c("M and 95% HDI are used to represent mean and the 95% high density interval, respectively. Values in square brackets represents the 95% HDI for the estimated parameter. All values are posterior estimates from the Bayesian Hierarchical Metacognition Model (HMM)."))


save_as_docx(print_table, path = here("tables", "hmm_mratio_table.docx"))
```
