---
title: "Fit Hierarchical Metacognition Model"
output: html_notebook
This script will fit the metacognition data from all four tasks in one group, using the HMetad approach (see Fleming 2017).
---
```{r}

# check for pacman package and install if not found
if (!require("pacman")) install.packages("pacman")
pacman::p_load(afex, readr, dplyr, tidyr, ggplot2, cowplot, devtools, here, tidyverse, magrittr, reshape2, rjags, coda, lattice, broom, ggmcmc, ggpubr, ggpol, patchwork, ggcorrplot, ggstatsplot, GGally)


# load the metaSDT package from github
if (!require("metaSDT")) devtools::install_github("craddm/metaSDT")

source(here("r", "remove_outliers_robust.R"))
source(here("r", "outliers.R"))
source(here("r", "trials2counts.R"))
source(here("r", "sdt_functions.R"))
source(here("r", "Function_metad_groupcorr.R"))
source(here("r", "BootCorci.R"))
source(here("r", "function_rhoPlot.R"))


# set apa theme for plots
apatheme=theme_bw()+ #theme
  theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        panel.border=element_blank(),
        axis.line=element_line(),
        text = element_text(size = 15),
        axis.title = element_text(size = 12))

```


Then get the data

```{r}

# read in the data

metacognition_trial_data <- read_csv(here("data_summary", "metacognition_TrialData_master.csv"), 
    col_types = cols(confidence = col_double(), 
        rt_conf = col_double()))

# set modality as factor
metacognition_trial_data$modality <- as.factor(metacognition_trial_data$modality )

# remove any rows containing NaNs (i.e., missing data)

metacognition_trial_data <- na.omit(metacognition_trial_data)

head(metacognition_trial_data)



metadata <- metacognition_trial_data %>%
  group_by(subject, modality) %>%
  mutate(rt = remove_outliers_robust(rt)) # remove RT outliers using MAD Rule - SEE PRE REG

metadata <- na.omit(metadata)

#Exclude those with rt <50ms 
metadata <- metadata%>%filter(rt>=0.05) 


#Exclude those with less than 50% trials (i.e. less than 100 or 50) within condition
metadata<-metadata%>%mutate(modality=as.factor(modality))
metadatac<-metadata #create new dataframe
metadatac$modality <-fct_collapse (metadatac$modality, trivia = c("Calories", "GDP"))#combine the two trivia tasks in new dataframe
metadatac <- metadatac %>%
  group_by(subject, modality)%>% count(subject) #count number of trials
excD <- subset(metadatac, metadatac$n<100) 
excID <-unique(excD$subject) #Identify participants for exclusion
metadata <- subset(metadata, !is.element(metadata$subject, excID)) ##Exclude IDs from that vector in original dataframe


```


Then fit the model

```{r}

subjects = unique(metadata$subject) # subjects vector, for looping
modalities = as.character(unique(metadata$modality)) # modalities vector, for

subjects <- subjects[-320]

#Loop over modalities and subjects to get into correct format for model. 

nR_S1 = list() 
nR_S2 = list()
      
for (m in 1:length(modalities)){
  
  nR_S1_tmp_modality = data.frame((matrix(NA, nrow=14, ncol=319)))
  nR_S2_tmp_modality = data.frame((matrix(NA, nrow=14, ncol=319)))

  for (s in 1:length(subjects)){
    

     subdata <- filter(metadata, subject == subjects[s] & modality == modalities[m])  
      
      #transform trial data to counts
      newlist <- trials2counts(subdata$signal, subdata$response, subdata$confidence, 7, padAmount = 1,padCells=1)
      nR_S1_tmp <- unlist(newlist[1], recursive = TRUE, use.names = TRUE)
      nR_S2_tmp <- unlist(newlist[2], recursive = TRUE, use.names = TRUE)
      
      nR_S1_tmp_modality[,s] <- nR_S1_tmp
      nR_S2_tmp_modality[,s] <- nR_S2_tmp
  
      
  } 
  nR_S1 [[m]]<- nR_S1_tmp_modality
  nR_S2 [[m]]<- nR_S2_tmp_modality

}

#Fit the hierarhical model and correlation
## NOTE THAT THIS WILL TAKE A LONG TIME - SEVERAL HOURS!
## First check if you already have the file. The file is too large for github, so first time 
## Users will need to download it from our OSF repo here: www.wwww..www

fit_filename = "/home/micah/metad_groupfit.RDS" ## change this to the correct place! 

if (file.exists(fit_filename) == 1 ) {

output <- readRDS(fit_filename)
  
}else  {
  
output <- metad_groupcorr(nR_S1, nR_S2)

}


#For Astrid: 

output <- readRDS("C:/Users/Astrid/Documents/DomainGen/modelfit.RDS")

```  

This next chunk pulls out the data from the model needed to plot HDI intervals, point estimates, and correlations. 
```{r}

## Model output ------------------------------------------------------------
# note that this section can take a while to run and creates a lot of large variables.


# Convergence diagnostic
Value <- gelman.diag(output, confidence = 0.95)
Rhat <- data.frame(conv = Value$psrf)

# Values (mean and CI)
Value <- summary(output)
stat <- data.frame(mean = Value$statistics[,"Mean"])
stat %<>%
  rownames_to_column(var = "name") %>% 
  cbind(CILow = Value$quantiles[,"2.5%"]) %>% 
  cbind(CIUp = Value$quantiles[,"97.5%"])

# HDI function 
HDI <- data.frame(HPDinterval(output, prob = 0.95))
HDI %<>%
  rownames_to_column(var = "name")


## Plot trace mcmc ---------------------------------------------------------
traceplot(output)

## Plot posterior distributions -------------------------------------------------------------------
mcmc.sample <- ggs(output)

```

Next, we plot the samples for point estimates of M-ratio together with the 95% HDI, seperate for each condition.

```{r}

#

memPlot <- mcmc.sample %>%
  filter(Parameter == "mu_logMratio[1]") %>% 
  ggplot(aes(exp(value))) +
  geom_histogram(binwidth = 0.01, fill = "blue", colour = "grey", alpha = 0.5) +
  geom_vline(xintercept = exp(stat$mean[stat$name == "mu_logMratio[1]"]),linetype="dashed", size = 1) +
  geom_segment(aes(x = exp(HDI$lower[HDI$name == "mu_logMratio[1]"]), y = 50, xend = exp(HDI$upper[HDI$name == "mu_logMratio[1]"]), yend = 50), colour = "white", size = 2.5) +
  apatheme +
  xlim(c(1, 1.25)) +
  ylim(c(0, 7000)) +
  ylab("Sample count") +
  ggtitle("Meta-Memory") +
  xlab(expression(paste(mu, " Mratio")))

calPlot <- mcmc.sample %>%
  filter(Parameter == "mu_logMratio[2]") %>% 
  ggplot(aes(exp(value))) +
  geom_histogram(binwidth = 0.01, fill = "blue", colour = "grey", alpha = 0.5) +
  geom_vline(xintercept = exp(stat$mean[stat$name == "mu_logMratio[2]"]),linetype="dashed", size = 1) +
  geom_segment(aes(x = exp(HDI$lower[HDI$name == "mu_logMratio[2]"]), y = 50, xend = exp(HDI$upper[HDI$name == "mu_logMratio[2]"]), yend = 50), colour = "white", size = 2.5) +
  apatheme +
  xlim(c(0.5, 1)) +
  ylim(c(0, 7000)) +
  ggtitle("Meta-Calories") +
  ylab("Sample count") +
  xlab(expression(paste(mu, " Mratio")))

gdpPlot <- mcmc.sample %>%
  filter(Parameter == "mu_logMratio[3]") %>% 
  ggplot(aes(exp(value))) +
  geom_histogram(binwidth = 0.01, fill = "blue", colour = "grey", alpha = 0.5) +
  geom_vline(xintercept = exp(stat$mean[stat$name == "mu_logMratio[3]"]),linetype="dashed", size = 1) +
  geom_segment(aes(x = exp(HDI$lower[HDI$name == "mu_logMratio[3]"]), y = 50, xend = exp(HDI$upper[HDI$name == "mu_logMratio[3]"]), yend = 50), colour = "white", size = 2.5) +
  apatheme +
  ggtitle("Meta-GDP") +
  xlim(c(1, 1.25)) +
  ylim(c(0, 7000)) +
  ylab("Sample count") +
  xlab(expression(paste(mu, " Mratio")))

visPlot <- mcmc.sample %>%
  filter(Parameter == "mu_logMratio[4]") %>% 
  ggplot(aes(exp(value))) +
  geom_histogram(binwidth = 0.01, fill = "blue", colour = "grey", alpha = 0.5) +
  geom_vline(xintercept = exp(stat$mean[stat$name == "mu_logMratio[4]"]),linetype="dashed", size = 1) +
  geom_segment(aes(x = exp(HDI$lower[HDI$name == "mu_logMratio[4]"]), y = 50, xend = exp(HDI$upper[HDI$name == "mu_logMratio[4]"]), yend = 50), colour = "white", size = 2.5) +
  apatheme +
  ggtitle("Meta-Vision") +
  xlim(c(0.5, 1)) +
  ylim(c(0, 7000)) +
  ylab("Sample count") +
  xlab(expression(paste(mu, " Mratio")))


(memPlot | calPlot) / (gdpPlot | visPlot)
# Plot posterior distribution for rho value

ggsave(here("figs", "mratio_hdi.png"))

```

Here we plot the same, but for the correlation (rho) estimate for each condition

```{r}

mcmc.rho <- mcmc.sample %>% 
  filter(Parameter == "rho[1]"| Parameter == "rho[2]"| Parameter == "rho[3]"| Parameter == "rho[4]"| Parameter == "rho[5]"| Parameter == "rho[6]")

meanRho <- mcmc.rho %>% group_by(Parameter) %>% summarise(value= mean(value, na.rm=TRUE)) 

H1title <- paste("Rho =",round(meanRho$value[1], digits=3))
H2title <- paste("Rho =",round(meanRho$value[2], digits=3))
H3title <- paste("Rho =",round(meanRho$value[3], digits=3))
H4title <- paste("Rho =",round(meanRho$value[4], digits=3))
H5title <- paste("Rho =",round(meanRho$value[5], digits=3))
H6title <- paste("Rho =",round(meanRho$value[6], digits=3))

Rho1 <- mcmc.sample %>% filter(Parameter == "rho[1]") 
Rho2 <- mcmc.sample %>% filter(Parameter == "rho[2]") 
Rho3 <- mcmc.sample %>% filter(Parameter == "rho[3]") 
Rho4 <- mcmc.sample %>% filter(Parameter == "rho[4]") 
Rho5 <- mcmc.sample %>% filter(Parameter == "rho[5]") 
Rho6 <- mcmc.sample %>% filter(Parameter == "rho[6]") 

#### NEED TO CHANGE RHO[1] in the FUNCTION!! 
R1 <- RhoPlot(Rho1, "rho[1]") + labs(title = "Memory and Calories", subtitle= paste(H1title))
R2 <- RhoPlot(Rho2, "rho[2]") + labs(title = "Memory and GDP", subtitle= paste(H2title))
R3 <- RhoPlot(Rho3, "rho[3]") + labs(title = "Memory and Vision", subtitle= paste(H3title))
R4 <- RhoPlot(Rho4, "rho[4]") + labs(title = "GDP and Calories", subtitle= paste(H4title))
R5 <- RhoPlot(Rho5, "rho[5]") + labs(title = "Calories and Vision", subtitle= paste(H5title))
R6 <- RhoPlot(Rho6, "rho[6]") + labs(title = "GDP and Vision", subtitle= paste(H6title))

#Bayesian Hierarhical fit: 
RhoPlot <- ggarrange(R1, R3, R2, R6, R4, R5)
annotate_figure(RhoPlot, top = text_grob("Hierarhical Bayesian estimation", color = "black", face = "bold", size = 14)) 

ggsave(here("figs", "mrho_grid.png"), height = 7, width = 12)
```

Now we will extract the individual participant level Mratio estimates and plot those to visualize the hierarchical correlation model. 

```{r}
# Create individual Mratio data frame
Mratio_indiv <- stat %>% 
  filter(grepl("^M", name)) %>% 
  mutate(task = ifelse(grepl("1]", name), "Mem",
                       ifelse(grepl("2]", name), "Cal",
                              ifelse(grepl("3]", name), "GDP","Vis"))),
         pp = name %>%
           str_extract(regex("\\d+(?=,)")) %>% 
           as.integer()) %>% 
  dcast(pp ~ task, value.var = "mean")

# Create plot
Cor1 <- Mratio_indiv %>% 
  ggplot(aes(x = Mem, y = Cal)) +
  geom_point(shape = 1) +
  geom_smooth(method = "lm", se = FALSE, colour = "black", size = 1) +
  apatheme +
  ggtitle("Mem-Cal")+
 #ylim(c(0.2, 2)) +
 # xlim(c(0.2, 2)) +
  ylab(expression(paste(mu, " Mratio"))) +
  xlab(expression(paste(mu, " Mratio")))

Cor2 <- Mratio_indiv %>% 
  ggplot(aes(x = Mem, y = GDP)) +
  geom_point(shape = 1) +
  geom_smooth(method = "lm", se = FALSE, colour = "black", size = 1) +
  apatheme +
  ggtitle("Mem-GDP")+
 # ylim(c(0.2, 2)) +
 # xlim(c(0.2, 2)) +
  ylab(expression(paste(mu, " Mratio"))) +
  xlab(expression(paste(mu, " Mratio")))

Cor3 <- Mratio_indiv %>% 
  ggplot(aes(x = Mem, y = Vis)) +
  geom_point(shape = 1) +
  geom_smooth(method = "lm", se = FALSE, colour = "black", size = 1) +
  apatheme +
 # ylim(c(0.2, 2)) +
 # xlim(c(0.2, 2)) +
  ggtitle("Mem-Vision")+
  ylab(expression(paste(mu, " Mratio"))) +
  xlab(expression(paste(mu, " Mratio")))

Cor4 <- Mratio_indiv %>% 
  ggplot(aes(x = Cal, y = GDP)) +
  geom_point(shape = 1) +
  geom_smooth(method = "lm", se = FALSE, colour = "black", size = 1) +
  apatheme +
  ggtitle("Cal-GDP")+
#  ylim(c(0.2, 2)) +
 # xlim(c(0.2, 2)) +
  ylab(expression(paste(mu, " Mratio"))) +
  xlab(expression(paste(mu, " Mratio")))

Cor5 <- Mratio_indiv %>% 
  ggplot(aes(x = Cal, y = Vis)) +
  geom_point(shape = 1) +
  geom_smooth(method = "lm", se = FALSE, colour = "black", size = 1) +
  apatheme +
  ggtitle("Cal-Vision")+
 # ylim(c(0.2, 2)) +
 # xlim(c(0.2, 2)) +
  ylab(expression(paste(mu, " Mratio"))) +
  xlab(expression(paste(mu, " Mratio")))


Cor6 <- Mratio_indiv %>% 
  ggplot(aes(x = GDP, y = Vis)) +
  geom_point(shape = 1) +
  geom_smooth(method = "lm", se = FALSE, colour = "black", size = 1) +
  apatheme +
  ggtitle("GDP-Vision")+
#  ylim(c(0.2, 2)) +
#  xlim(c(0.2, 2)) +
  ylab(expression(paste(mu, " Mratio"))) +
  xlab(expression(paste(mu, " Mratio")))


plot_grid(Cor1, Cor2, Cor3, NULL, Cor4, Cor5, NULL, NULL, Cor6, 
          labels = c("A", "B", "C", "", "D", "E", "", "", "F"), nrow = 3, ncol = 3)


ggsave(here("figs", "mrho_scatter_grid.png"), height = 7, width = 12)
```

```{r}
write.csv(Mratio_indiv, here("data_summary", "MRatio_GroupEst.csv"))
```



